Model LF

### 2022-09-26 Estimation.Rmd
Opdateret participation equation

```{r}
#empl = N/1000
#empl_ds = Nadj/1000
 wage = w_h_r/emp
# wage = w_h_rk_ds /(empl_ds)
 Nu=(w_row_r - w_row_p)/wage
 Nf = Nu + emp
 prod = y/Nf
 LF = unemp + emp
 lfadj = unempadj + empadj
 ur = unemp/LF
 ur_ds = unempadj/lfadj
# yk = y/(py/100)
 prodk = yk/Nf
 yf = w + b2
 ws = w/yf
 ps = 1 - ws
# w = w_h_r + (W_row_r - W_row_p)
 fdis = yf/y
 urterm = ur - urs
 wageindex = wage/wage[22] #element from 2010Q3
 priv = pconk + ik + xk
 part = LF*1000/pop
 old_age_ratio = retired_pop/pop
 zaland_jesper = pop - LF*1000  
 nben_h = nsben_h + d8_h
```

@@

```{r}
reg_part_start=dynlm(TSDELTALOG(part) ~ 1 + L(TSDELTALOG(part),1:4) +  L(TSDELTALOG(komp_r_obs),0:4)+  L(TSDELTALOG(rw_ds),0:4) + L(TSDELTA(ur_ds),0:4)+ L(log(part),1) + L(log(komp_r_obs),1) + L(log(rw_ds),1) + L((ur_ds),1) + d_2013q4)

@@

```{r}
 komp_r_vars_1 <- str_c("L(TSDELTALOG(komp_r_obs), 0:4)", c(1,2,4))
 part_vars_1 <- str_c("L(TSDELTALOG(part), 1:4)", c(1,3,4))
 rw_ds_vars_1 <- str_c("L(TSDELTALOG(rw_ds), 0:4)", c(0,2,3,4))
 ur_ds_vars_1 <- str_c("L(TSDELTA(ur_ds), 0:4)", c(0,1,2,3,4))
```

@@

```{r}
reg_part=dynlm(TSDELTALOG(part) ~ 1 + L(TSDELTALOG(part),2) +  L(TSDELTALOG(komp_r_obs),c(0,3))+  L(TSDELTALOG(rw_ds),1) + L(log(part),1) + L(log(rw_ds),1) + L((ur_ds),1) + d_2013q4)

>>>>

```{r}
#empl = N/1000
#empl_ds = Nadj/1000
 wage = w_h_r/emp
# wage = w_h_rk_ds /(empl_ds)
 Nu=(w_row_r - w_row_p)/wage
 Nf = Nu + emp
 prod = y/Nf
 LF = unemp + emp
 lfadj = unempadj + empadj
 ur = unemp/LF
 ur_ds = unempadj/lfadj
# yk = y/(py/100)
 prodk = yk/Nf
 yf = w + b2
 ws = w/yf
 ps = 1 - ws
# w = w_h_r + (W_row_r - W_row_p)
 fdis = yf/y
 urterm = ur - urs
 wageindex = wage/wage[22] #element from 2010Q3
 priv = pconk + ik + xk
 part = LF*1000/pop
 old_age_ratio = retired_pop/pop
 part1= LF*1000/(pop*(1-old_age_ratio))
 zaland_jesper = pop - LF*1000  
 nben_h = nsben_h + d8_h
```

@@

```{r}
reg_part_start=dynlm(TSDELTALOG(part1) ~ 1 + L(TSDELTALOG(part1),1:4) +  L(TSDELTALOG(komp_r_obs),0:4)+  L(TSDELTALOG(rw_ds),0:4) + L(TSDELTA(ur_ds),0:4)+ L(log(part1),1) + L(log(komp_r_obs),1) + L(log(rw_ds),1) + L((ur_ds),1) + d_2013q4)

@@

```{r}
 komp_r_vars_1 <- str_c("L(TSDELTALOG(komp_r_obs), 0:4)", c(1,2,4))
 part_vars_1 <- str_c("L(TSDELTALOG(part1), 1:4)", c(1,3))
 rw_ds_vars_1 <- str_c("L(TSDELTALOG(rw_ds), 0:4)", c(2,3,4))
 ur_ds_vars_1 <- str_c("L(TSDELTA(ur_ds), 0:4)", c(0,1,2,4))
```

@@

```{r}
reg_part=dynlm(TSDELTALOG(part1) ~ 1 + L(TSDELTALOG(part1),c(2,4)) +  L(TSDELTALOG(komp_r_obs),c(0,3))+  L(TSDELTALOG(rw_ds),0:1) + L(TSDELTA(ur_ds),3)+ L(log(part1),1) + L(log(komp_r_obs),1) + L(log(rw_ds),1) + L((ur_ds),1) + d_2013q4)

### 2022-09-26 max_dp endogen stød.Rmd
Opdateret participation equation

BEHAVIORAL> part1
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(part1) = beta_0 + beta_1*TSDELTALOG(TSLAG(part,2)) + beta_2*TSDELTALOG(TSLAG(part,4)) + beta_3*TSDELTALOG(komp_r) + beta_4*TSDELTALOG(TSLAG(komp_r,3)) +beta_5*TSDELTALOG(rw_ds) + beta_6*TSDELTALOG(TSLAG(rw_ds,1)) + beta_7*TSDELTA(TSLAG(ur_ds,3)) + beta_8*LOG(TSLAG(part1,1))  + beta_9*log(TSLAG(rw_ds,1)) + beta_10*log(TSLAG(komp_r,1)) + beta_11*TSLAG(ur_ds,1) + beta_12* d_2013q4
COEFF> beta_0 beta_1 beta_2 beta_3 beta_4 beta_5 beta_6 beta_7 beta_8 beta_9 beta_10 beta_11 beta_12
STORE> coe(16)

@@

   sens1 = TIMESERIES(c(sens1),   
                       START=c(2006,1),FREQ=4),

@@

@@

@@

@@

plot(max_dp_02, col= "red"); lines(max_dp_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_02, col= "red"); lines(wage_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(komp_r_02, col= "red"); lines(komp_r_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(part_02, col= "red"); lines(part_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(pc_ds_02, col= "red"); lines(pc_ds_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(emp_02, col= "red"); lines(emp_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

>>>>

BEHAVIORAL> part1
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(part1) = beta_0 + beta_1*TSDELTALOG(TSLAG(part1,2)) + beta_2*TSDELTALOG(TSLAG(part1,4)) + beta_3*TSDELTALOG(komp_r) + beta_4*TSDELTALOG(TSLAG(komp_r,3)) +beta_5*TSDELTALOG(rw_ds) + beta_6*TSDELTALOG(TSLAG(rw_ds,1)) + beta_7*TSDELTA(TSLAG(ur_ds,3)) + beta_8*LOG(TSLAG(part1,1))  + beta_9*log(TSLAG(rw_ds,1)) + beta_10*log(TSLAG(komp_r,1)) + beta_11*TSLAG(ur_ds,1) + beta_12* d_2013q4
COEFF> beta_0 beta_1 beta_2 beta_3 beta_4 beta_5 beta_6 beta_7 beta_8 beta_9 beta_10 beta_11 beta_12
STORE> coe(16)

@@

   sens1 = TIMESERIES(c(sens1),   
                       START=c(2005,2),FREQ=4),

@@

## update model data
```{r}

#S_modelData$sens1 = sens1

@@

emp_01w = Shock_1wage$simulation$emp

@@

### Compare with shock 1

@@

plot(max_dp_02, col= "red"); lines(max_dp_01w, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_02, col= "red"); lines(wage_01w, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(komp_r_02, col= "red"); lines(komp_r_01w, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(part_02, col= "red"); lines(part_01w, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(pc_ds_02, col= "red"); lines(pc_ds_01w, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(emp_02, col= "red"); lines(emp_01w, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
